A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-03-28 doc/draft-01-stokes/05conclusion.tex
first pass at abstract

There are some interesting questions to answer
on the use of Fredholm determinants in numerical
calculations.
%
As observed in \cite{zhao2015robust}, the
combined-field representation causes some
difficulty in that the Fredholm determinant
is not defined when the single layer, which
is not trace-class, is included.
%
Zhao and Barnett~\cite{zhao2015robust}
suggest looking into
representations of the form $\cI-2\cD
-2i\eta\cS^2-2\cW$,
which would have a well-defined Fredholm
determinant.
%
The relative performance of
such an approach should be explored.
%
Further, as discussed above, the
convergence of the determinant of
integral equations discretized with
panel-corrected schemes (as described in
\cref{sec:numerical}) is yet to be proved.
%
Finally, it is worth exploring alternatives
to the Fredholm determinant which perform well
for layer potentials that are not trace class
on the boundary.

>>>>

There are some interesting questions to answer
on the use of Fredholm determinants in numerical
calculations.
%
As observed in \cite{zhao2015robust}, the
combined-field representation causes some
difficulty in that the Fredholm determinant
is not defined when the single layer, which
is not trace-class, is included.
%
Zhao and Barnett~\cite{zhao2015robust}
suggest looking into
representations of the form $\cI-2\cD
-2i\eta\cS^2-2\cW$,
which would have a well-defined Fredholm
determinant.
%
The relative performance of
such an approach should be explored.
%
Further, as discussed above, the
convergence of the determinant of
integral equations discretized with
panel-corrected schemes (as described in
\cref{sec:numerical}) is yet to be proved.
%
When addressing high frequency problems,
the fast-direct solver used to evaluate
determinants in this paper will no longer
have near-linear scaling~\cite{ho2012fast}.
%
The design of fast-direct solvers in this
regime is the subject of ongoing research, and
to the best of our knowledge, fast determinant
computation at high frequency is an open
question.
%
Finally, it is worth exploring alternatives
to the Fredholm determinant which perform well
for layer potentials that are not trace class
on the boundary or for problems at higher
frequencies.

### 2019-03-28 doc/draft-01-stokes/stokes-eig.tex
first pass at abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abstract{The Stokes eigenvalue problem is a common
  model problem in the numerical analysis of
  the eigenvalues of higher-order partial differential
  equations.
  }

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abstract{The boundary integral equation (BIE) framework
  provides robust and scalable eigenvalue computations, which
  owes to the fact that only the boundary of the domain
  must be discretized and that there is no high frequency
  ``pollution'' when using a Green's function to analytically
  represent the propagation of oscillatory waves.
  %
  In this paper, we detail the theoretical justification
  for a BIE approach to the Stokes eigenvalue problem on
  simply and multiply-connected planar domains, which entails
  a treatment of the uniqueness theory for oscillatory
  Stokes equations on exterior domains. 
  %
  Then, using well-established techniques for
  discretizing BIEs and fast linear algebra,
  we present numerical results which confirm
  the analytical claims of the paper and demonstrate
  the efficiency of the overall approach.
}
